\subsection{REST API Summary}

The rest API is studied to experiment with multiple different approaches to the REST paradigm. More in detail, endpoints associated with rides and devices are developed in a more traditional way, with the entirety of the information needed to satisfy the request directly in the URI.
Other endpoints require additional information (such as the type of operation required) as additional parameters in the request.\\

Part of the URIs are filtered through different filters. M indicates that only users with the role of Manager can access to the endpoint, E indicates that only editors can access the endpoint, A that only administrators can request the specified URI to the server.


\begin{longtable}{|p{.335\columnwidth}|p{.1\columnwidth} |p{.39\columnwidth}|p{.1\columnwidth}|} 
\hline
\textbf{URI} & \textbf{Method} & \textbf{Description} & \textbf{Filter} \\\hline
user/login/                        & POST   & Enables passing the web server the credential of a user. If the credentials are correct it provides a JWT token. & U \\ \hline
user/register/                     & POST   & Enables a user to register for the app. & U \\ \hline
user/logout/                       & POST   & Logout a user & U \\ \hline
user/delete/{userid}               & DELETE & Enables an authenticated user to delete his account. Login information should be given again before proceeding to the deletion. & U \\ \hline
user/update/{userid}               & GET    & Enable an authenticated user to update his personal information. & U \\ \hline
user/update/{userid}/password      & POST   & Enable an authenticated user to update his password & U \\ \hline
user/{userid}                      & POST   & Get user information & U \\ \hline
template/                          & GET    & Get templates to use for a workspace & U \\ \hline
template/create                    & POST   & returns the data for a specific park, given the name as URL parameter. & U  \\ \hline
template/delete/{templateid}       & DELETE & Returns the list of all parks in the database & U  \\ \hline
template/update/{templateid}       & PUT    & Returns the structure used to initialize the homepage. & U  \\ \hline
user/{userid}/workspaces           & GET    & Allows to insert a park passed as data & U  \\ \hline
workspace/{workspaceid}            & GET    & Allows to update a park passed as data & U  \\ \hline
workspace/create/{workspaceid}     & POST   & Allows to delete a park passed as data & U  \\ \hline
workspace/delete/{workspaceid}     & DELETE & Allows to get information on a specific user & M \\ \hline
workspace/update/{workspaceid}     & PUT    & Allows to update the information on a specific user & M \\ \hline
workspace/adduser                  & POST   & Allows to delete a user & M \\ \hline
workspace/removeuser               & DELETE & Enable the manager of a workspace to remove someone from the workspace & M \\ \hline
workspace/assignuserpermission     & POST   & Enable the manager of a workspace to assign different kinds of permissions to a user in a workspace & U \\ \hline
board/{boardid}                    & GET    & Returns all the information related to a board & M \\ \hline
workspace/{workspaceid}/boards     & GET    & Returns all the boards related to a workspace & M \\ \hline
board/create                       & POST   & Allows manager and editor of a workspace to create a board & E \\ \hlinee
board/delete/{boardid}             & DELETE & Allows to pass to the ws of a usnd their mail and password correspond. & E \\ \hlinee
board/update/{boardid}             & PUT    & Allows manager and editor of a workspace to edit a board by \{board id\} & E \\ \hlinee
subboard/{subboardid}              & GET    & Allows manager and editor of a workspace to delete a board by \{board id\}  & U \\ \hline
board/{boardid}/subboards          & GET    & Returns all subboard data belonging to the current board & U \\ \hline
subboard/create                    & POST   & Allows to create a new subboard & E \\ \hlinee
subboard/delete/{subboardid}       & DELETE & Allows to delete the subboard by its \{subboard id\} & E \\ \hlinee
subboard/update/{subboardid}       & PUT    & Allows to update the subboard by its \{subboard id\}& U \\ \hline
subboard/{subboardid}/activities   & GET    & Returns all activitydata belonging to the current subboard with the \{subboard id\}  & U \\ \hline
activity/{activityid}              & GET    & Returns all subboard data by its  \{activity id\} & U \\ \hline
activity/create                    & POST   & Allows to create a new activity & U \\ \hline
activity/delete/{activityid}       & DELETE & Allows to delete the activityby its \{activity id\} & U \\ \hline
activity/update/{activityid}       & PUT    & Allows to update the activityby its \{activity id\}  & U \\ \hline
activity/assignee/get              & GET    & Returns the assignee data of the current activity & U \\ \hline
activity/assignee/add              & PUT    & Allows to insert new assignee of the current activity & U \\ \hline
activity/assignee/remove           & POST   & Allows to delete assignee of the current activity & U \\ \hline
activity/comment/get               & GET    & Returns comment  & U \\ \hline
activity/comment/create            & PUT    & Allows to create new comment & U \\ \hline
activity/comment/delete/{commentid}& DELETE & Allows to insert comment by its \{comment id\} & U \\ \hline
activity/comment/update/{commentid}& PUT    & Allows to update comment by its \{comment id\}  & U \\ \hline
analytics/get                      & GET    & Returns analytics data. & M \\ \hlinee
\caption{Main REST API entrypoints}

\begin{itemize}
\item M-Only manager 
\item U-All user
\item E-Editor 
\end{itemize}


\label{tab:termGlossary}
\end{longtable}